---
title: "Multiple Factor Analysis"
author: "Jigncheng Xu, Matthew Rainey, Cristian Garay, and Sai Dulla"
date: "November 29, 2016"
output: ioslides_presentation
---

## Multiple Factor Analysis

MFA is used when several sets of variables have been measured on the same set of observations.
The number and/or nature of the variables used to describe the observations can vary from one 
set of variables to the other, but the observations should be the same in all the data sets.

The goals of MFA:

- to analyze several data sets measured on the same observations
- to provide a set of common factor scores i.e compromise factor scores
- to project each of the original data sets onto the compromise to analyze
  commonalities and discrepancies

## The Steps of MFA: 

- Step 1: Calculate PCA of each Data Table
- Step 2: Creating the α Weight Vector
- Step 3: Generalized PCA of X

## Performing MFA with MFA package
To perform MFA, use the `mfa` function:
```{r}
library(MFA)
result <- mfa(wines, sets)
result
```

## The MFA Object
The result from `mfa` function is a list of eigenvalues, (compromise)
factor scores, variable loadings, partial factor scores and weights.
```{r}
summary(result)
```

## Factor Scores
Factor scores are the coordinates of the data in the new "dimensions".

To visualise the factor scores, use `PlotFactorScores`
function.

## Factor Scores (continued)
```{r}
PlotFactorScores(result, group = wines$country, label = wines$ID)
```

## Loadings
Variable loadings reflects the importance of that variable for this
component and can also be used to plot maps of the variables that
reflect their association.

`PlotLoadings` plots the variable loadings.

## Partial Factor Scores
Partial factor scores are the positions "as seen by" each data set
(sub-table). Partial factor scores is stored as a list of matrices in
the mfa object.

To visualise the partial factor scores, use `PlotPartialFactorScores`
function (here we are plotting the second and third dimensions).

## Partial Factor Scores (continued)
```{r}
PlotPartialFactorScores(result, 1, group = wines$country, label = wines$ID, dim = c(2, 3))
```

## Eigenvalues
In MFA, the importance of a dimension is reflected by its eigenvalue
which indicates how much of the total inertia of the data is explained by that component.

To get a summary for the eigenvalues, use `EigSummary` function.

## Eigenvalues (continued)
```{r}
EigSummary(result)
```

## Eigenvalues (continued)
To visualise the eigenvalues, use `PlotEig`:
```{r}
PlotEig(result)
```

## Contributions
- The contributions of an observation tells us how much each
  observation contributes to a dimension.
- The contributions of a variable tells us how much each variable
  contributes to a dimension.
- The contribution of a table to tells us how much all of the
  variables in a given table contribute to a dimension.

For these 3 types of contributions, use `ContribObs`, `ContribVar`,
and `ContribTable` functions.

## Contributions (continued)
The following code computes the contribution of tables to the first 3 dimensions.
```{r}
ContribTable(result)[, 1:3]
```

## Coefficients for Between-Table Structure
- To judge how similar two tables are, we can use the RV or Lg coefficients.
- The RV coefficient represents the correlation between two tables.
- The RV coefficient is always between 0 and 1.
- The Lg coefficient reflects the MFA normalization between two tables.
- For both coefficients, The larger the coefficient, the more similar the two tables are.

We can calculate these with the `RV`, `RV_table`, `Lg`, and `Lg_table` functions

## Coefficients (continued)
The following code computes the Lg Coefficients between the first 4 tables.
```{r}
Lg_table(wines, sets)[1:4, 1:4]
```

## Bootstrap
Bootstrap ratios, like t-statistics, can be used to find observations
that reliably contribute to a given component. It is obtained by
dividing each bootstrap mean by its standard deviation.

To compute bootstrap ratios, use `BootstrapRatios` function.

## Bootstrap (continued)
The following code computes the bootstrap ratios for the first 7
observations and first 2 components.
```{r}
BootstrapRatios(result)[1:7, 1:2]
```
