---
title: "Performing MFA"
author: "Jingcheng Xu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Performing MFA}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
This vignette is about using this package to perform MFA (Multiple Factor Analysis), get summaries for the result, and plot the results.  MFA is used when several sets of variables have been measured on the same set of observations.

## Performing MFA
To perform MFA, use the `mfa` function:
```{r}
library(MFA)
result <- mfa(wines, sets)
```

Here `wines` is a data set included in the package, and `sets` is a
list of integer vectors representing the subtables in the `wines` data set.

```{r}
result
summary(result)
```

`result` is an object of class `mfa` which is a list with several
elements.  `eig` holds the eigenvalues, which measure the importance
of each dimension (or component) by describing how much of the inertia
of the data is explained by that dimension.  The `factor.scores` is a
matrix that represents a compromise for the tables, and describe the
observations.  The `partial.factor.scores` are the same, but only
represent a single table.  The `loadings` holds a matrix that
describes the individual variables.

## Summaries of the eigenvalues

The summaries of the eigenvalues will describe how much of the inertia
each eigenvaue explains.  To get the summaries of eigenvalues of the
result, we can use `EigSummary`:
```{r}
EigSummary(result)
```

## Plotting the results
There are 4 functions that can be used to visualise the result.

The `PlotEig` function gives a bar chart of the eigenvalues.

The `PlotFactorScores` function plots the factor scores of the result
from MFA. The argument `group` can be used to provide grouping
(different colouring) on the plot.

The `PlotPartialFactorScores` function is similar, only requiring one
more argument to specify the particular table.

The `PlotLoadings` function plots the variable loadings. Similar to
the other two functions, `var.group` argument can be used to provide
grouping among variables.

```{r, fig.width=7, fig.height=7}
PlotEig(result)
PlotFactorScores(result, group = wines$country, label = wines$ID)
PlotPartialFactorScores(result, 1, group = wines$country, label = wines$ID, dim = c(2, 3))
PlotLoadings(result)
```

## Related functions
### Contributions

To understand how much each observation, variable and table
contributes to each dimension, we compute the contribution for each.
All of the contributions for a given dimension must add to one.

With our wine data, each observation is a different wine, each table
corresponds to an assessor and each variable is an assessors grade
given to the wine on certain criteria.

### Contribution of an Observation to a Dimension

The contributions of an observation tells us how much each observation
contributes to a dimension.  To get the Contributions of an
Observation, use the `ContribObs` function.  The output given will
have the columns represent dimensions and the rows represent
observations.  Using the wine data as an example:
```{r}
ctr.obs <- ContribObs(result)
ctr.obs[,1:3]
```

Since we have 12 wines (observations), we get a sense of how much an
observation contributes by it's contributions size relative to 1/12.
For example, the tenth wine contributes a lot to the second dimension,
but very little to the first or third.

### Contributions of a Variable to a Dimension

The contributions of a variable tells us how much each variable
contributes to a dimension.  To get the Contributions of a Variable,
use the `ContribVar` function. The output has columns representing
dimensions and rows representing variables.  With the wine data as an
example:
```{r}
ctr.var <- ContribVar(result)
ctr.var[1:8, 1:3]
```

We have 53 variables, so we get a sense of how much a variable
contributes by it's contributions size relative to 1/53.  For example,
the third variable contributes a lot to the second dimension but very
little to the third.

### Contributions of a Table to a Dimension

The contribution of a table to tells us how much all of the variables
in a given table contribute to a dimension.  To get the Contributions
of a Table, use the `ContribTable` function. The output has columns
representing dimensions and rows representing Tables.  With the wine
data as an example:
```{r}
ctr.table <- ContribTable(result)
ctr.table[, 1:3]
```

There are 10 assessors (tables), so we get a sense of how much a table
contributes by it's contributions size relative to 1/10.  For example
the fifth assessor contributes a lot to the third dimension, but only
a small amount to the second.


### Bootstrap
The package also included a function `BootstrapRatios` for computing
the bootstrap ratios, which can be used to find observations that
reliably contribute to a given component. Here the ratios are computed
by dividing each bootstrap mean by its standard deviation.
```{r}
BootstrapRatios(result, times = 2000)
```
